Analysis : exp234-242 g_Ca dynamic reactivation

### 2019-06-07 resistingrhythm/analysis/exp234_242.Rmd
....

---
title: "Analysis : exp220 - 228 (Nov 2018, for J Neurophys draft 2018)"
output: html_notebook
---

@@

# Load all data
```{r, message=FALSE}
# -----------------------------------------------------------------------
# 16: Burst E, with H
exp_code <- 224
osc_codes <- c(100, 101, 102, 103, 104, 105, 110, 115, 120, 125, 130)
osc_rates <- c(0, 0.1, 0.2, 0.3, 0.4, 0.5, 1.0, 1.5, 2.0, 2.5, 3.0)
stim_codes <- c(3, 4) # 4

>>>>

---
title: "Analysis : exp234-242 g_Ca dynamic reactivation"
output: html_notebook
---

@@

# Load all data

I turned d(g_Ca)/dt back on but don't have record of confirming everything way. I've been using sims without it...
```{r, message=FALSE}
# -----------------------------------------------------------------------
# 16: Burst E, with H
exp_code <- 238
osc_codes <- c(100, 101, 102, 103, 104, 105, 110, 115, 120, 125, 130)
osc_rates <- c(0, 0.1, 0.2, 0.3, 0.4, 0.5, 1.0, 1.5, 2.0, 2.5, 3.0)
stim_codes <- c(3, 4) # 4
